NGO analysis

### 2022-07-28 Dashboard/Dashboard data tests.Rmd
Discovered setequal().

## Functions to read Excel file ------------------------------------------------
widen_excel_test <- function(file) {
  read_excel(file) |> 
    # cleaning names to enable later operations
    clean_names()
}

widen_excel <- function(object) {
  if ("year" %in% names(object) && "firm" %in% names(object) &&
    "category" %in% names(object) && "sub_category" %in% names(object) &&
    "name" %in% names(object) && "value" %in% names(object)) {
    object |>
      # uniting category and name to deal with multiple 'Other'
      unite(
        entry, c(category, name)
      ) |>
      # deleting Sub-category and Firm
      select(-sub_category, -firm) |>
      # pivoting to create 'tidy' variables
      pivot_wider(names_from = entry, values_from = value) |>
      # cleaning names
      clean_names()
  } else {
    validate("Please upload data using the specified Excel template.")
  }
}

>>>>

## Functions to read Excel file ------------------------------------------------
widen_excel_test <- function(file) {
  # Reading Excel file
  read_excel(file) |> 
    # cleaning names to enable later operations
    clean_names()
}

widen_excel <- function(object) {
  # testing if all columns are present
  if (setequal(names(object),
               c("year", "firm", "category", "sub_category", "name", "value"))) {
    object |>
      # uniting category and name to deal with multiple 'Other'
      unite(
        entry, c(category, name)
      ) |>
      # deleting Sub-category and Firm
      select(-sub_category, -firm) |>
      # pivoting to create 'tidy' variables
      pivot_wider(names_from = entry, values_from = value) |>
      # cleaning names
      clean_names()
  } else {
    validate("Please upload data using the specified Excel template.")
  }
}
